### 2017-03-08 Objects/Objects.tex
Fixing spacing in itemize env and really sorting the page numbering
Final bits before submission

For a particle to be identified as an electron it 
must also be reconstructed as an electron by the \ac{PF} algorithm, 
and must in addition pass more advanced identification criteria based on some of the variables used in the
standalone electron reconstruction. This provides separation power from backgrounds
such as photon conversions, jets misidentified as electrons, or electrons from b- and c-quark
decays. Both a cut-based algorithm and an algorithm based on \acp{BDT} are available. %FIXME define BDT
For the selection of electrons in 
the analyses presented in later chapters the \ac{BDT}-based algorithm is used, 
with exceptions for the loose identification criteria required for vetoing electrons. 
The variables used in this \ac{BDT} include:%FIXME full stop usage?!
\begin{itemize}
\setlength{\itemsep}{-\baselineskip}
\item Cluster shape variables, such as $\sigma_{i\eta,i\eta}$, the energy-weighted width of the supercluster in units of $\eta$ crystals (illustrated in figure \ref{fig:ele_id_vars}a). 
\item Track quality variables.
\item Distances in $\eta$ and $\phi$ between the supercluster and the associated track.
\item Energy ratios and energy-momentum ratios in the region of the supercluster, including
$1/E_{\text{SC}} - 1/p_{\Pe}$, where $E_{\text{SC}}$ is the energy in the supercluster and $p_{\Pe}$ the momentum of the electron track (illustrated in figure \ref{fig:ele_id_vars}b).
%\item Cluster shape variables $\sigma_{i\eta,i\eta}$ and $\sigma_{i\phi,i\phi}$, with $i\eta$ and $i\phi$ the integer
%label of the $\eta$ and $\phi$ calorimeter cell. The circularity =  $1 -\frac{E1\times5}{E5\times5}$, with
%$E1\times5$ and $E5\times5$ the energies in a $1\times5$ and a $5\times5$ grid around the super cluster seed,
%respectively. Shape variable R9 = $\frac{E3\times3}{E_{SC}}$, with $E3\times3$ the energy in a $3\times3$ grid
%of cells around the super cluster seed and $E_{SC}$ the raw energy of the super cluster.
%\item The number of valid hits in the track fit, the $\chi^2$ of the track fit and the $\chi^2$ of the GSFTrack fit
%%\item The number of GSFtrack hits, the number of expected missing inner hits and the result of the conversion vertex fit
%\item The distance $\Delta \eta$ and $\Delta \phi$ between the reconstructed super cluster and the associated track at the position of the primary vertex, and the distance in $\eta$ between the super cluster and the track at the calorimeter surface.
%\item H/E, the ratio of the hadronic energy over the electromagnetic energy in the super cluster and E/P, the ratio of the super cluster energy over the momentum of the track associated with the electron
%\item The ratio of the energy of the electron cluster and the momentum of the associated track, evaluated at the electron cluster,
% and $1/E_e - 1/P_e$, with $E_e$ the energy of the electron candidate and $P_e$ its momentum.
\end{itemize}
%Figure \ref{fig:ele_id_vars} shows the distributions of $\sigma_{i\eta,i\eta}$ and $1/E_{sc} - 1/p_e$ 
%for real and misidentified electrons in the full dataset from the 2012 running period of the \ac{LHC}.

\begin{figure}[h!]
\begin{center}
\subfloat[$\sigma_{i\eta,i\eta}$]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/Sigmaietaieta.png}}
\subfloat[$1/E_{\text{SC}} - 1/p_{e}$]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/OneoverEminOneoverp.png}}
\end{center}
\caption[$\sigma_{i\eta,i\eta}$ and $1/E_{\text{SC}}-1/p_{e}$ for real 
and misidentified electrons at $8\,\TeV$, for data and simulation]{(a) $\sigma_{i\eta,i\eta}$ and (b) $1/E_{\text{SC}} - 1/p_{e}$ for real (black points)  and 
misidentified (yellow triangles) electrons in a dataset corresponding to $19.7\,\invfb$
taken at $\sqrt{s} = 8\,\TeV$, overlaid on the distributions for simulated 
real electrons in purple \cite{cms-elereco-run1}.}
\label{fig:ele_id_vars}
\end{figure}

@@

For the analysis presented in chapter \ref{chap:mssm}, ``medium'' muon requirements were applied \cite{CMS-PAS-HIG-16-037}.
These requirements include:
\begin{itemize}
\setlength{\itemsep}{-\baselineskip}
\item Reconstruction by either the global or tracker muon reconstruction algorithms.
\item Requirements on track quality, and compatibility between the tracker track and the muon system track.
\item Selection on the segment compatibility, a weight between 0 and 1 which is a measure of the compatibility
of a track with the muon track segments in the muon stations it has crossed.
\item Requirements on the maximum kink in the tracker track in any of the layers of the tracker, to suppress in-flight decays.
\end{itemize}
%Apart from having passed either the global or tracker muon reconstruction, the selection
%includes a threshold on the fraction of valid tracker hits, requirements on the
%$\chi^2$/$N_{\text{dof}}$ of the global track fit, on the compatibility of the tracker- and standalone-reconstructed
%position matching, on the kink finder in the inner tracker, and the segment compatibility. 
%The compatibility of the tracker- and standalone-reconstructed position is evaluated
%by extrapolating both the muon track and the tracker track to the same surface and evaluating the $\chi^2$ 
%compatibility there.
%The kink finder determines the $\chi^2$ compatibility between the positions of the outward- and inward interpolated
%tracks in each layer of the inner tracker. The largest $\chi^2$ value found at any of the tracker layers 
%is used as a discriminator. If the $\chi^2$ value is large, this could signal an in--flight decay.
%The segment
%compatibility is a weight between 0 and 1 which is a measure of the compatibility of a track with
%the muon track segments in muon stations it has crossed. Numbers closer to 1 represent
%a greater compatibility of the track with the muon segments, and therefore with the track belonging to a muon.
%MEDIUM REQUIREMENTS
%To pass the identification, global- or tracker muons
%with a large enough fraction of tracker hits must pass \textbf{either} 
%\begin{itemize}
%\setlength{\itemsep}{-\baselineskip}
%\item The muon is reconstructed by the global muon reconstruction algorithm
%\item The $\chi^2$/$N_{\text{dof}}$ of the global track fit, using both the tracker and muon system hits, should be less than 3
%\item The $\chi^2$ compatibility of the tracker-standalone position is smaller than 12
%\item The $\chi^2$ compatibility of the kink finder in the tracker is less than 20
%\item The segment compatibility is $>$ 0.303
%\end{itemize}
%\textit{or}:
%\begin{itemize}
%\setlength{\itemsep}{-\baselineskip}
%\item The segment compatibility is $>$ 0.451
%\end{itemize}

@@

The \ac{PF} algorithm starts from charged particle tracks measured
by the inner tracker, muon tracks measured in the muon system, and 
energy deposits in the calorimeters. These energy deposits are combined
using a clustering algorithm, so that stable neutral particles can be identified and
separated from charged hadrons, and in addition electrons and all bremsstrahlung photons
can be reconstructed. Clustering is performed separately in the \ac{ECAL} barrel,
\ac{ECAL} endcaps, first and second \ac{PS} layers, \ac{HCAL} barrel and \ac{HCAL} endcaps, with no 
clustering employed in the \ac{HF}.
%And to aid energy measurement of charged hadrons for which
%tracks were low quality, or high pT
The clustering algorithm used for \ac{PF} starts from cluster seeds,
calorimeter cells with local energy maxima. Topological clusters are built by 
merging neighbouring cells into the cluster, provided that the cells
being merged in contain a certain minimum energy.
The threshold is $800\,\MeV$ in the \ac{HCAL} and two standard deviations above the
expected noise level in the \ac{ECAL}, meaning $80\,\MeV$ in the barrel and up 
to $300\,\MeV$ in the endcaps. Cell energies can be shared between multiple
\ac{PF} clusters, depending on the distance between a cell and the centre of the cluster.

Any given particle will usually give rise to multiple \ac{PF}
elements in the different subdetectors. To provide full reconstruction
of each particle, and avoid double counting, the next step in the
\ac{PF} algorithm is to link the different elements. This is
achieved by defining a distance parameter between any two \ac{PF} elements
in the event, which quantifies the link quality. Directly and indirectly
linked elements are considered as input blocks to the reconstruction and
identification algorithm. Links between charged tracks and calorimeter
clusters are established by extrapolating the track from its last measured
tracker hit to the \ac{PS} layers, the \ac{ECAL} and the \ac{HCAL}. %in ECAL to expected maximum of a 
%typical longitudinal electron shower profile and in the HCAL at a depth correspnding to one interaction
%length.
If the extrapolated track position is within the boundaries of the cluster, plus the size
of one cell in each direction to account for gaps between cells and multiple scattering, the
track is said to be linked to the calorimeter cluster. The link distance parameter 
is taken as the distance $\Delta R$ 
between the position of the cluster and the position of the track. Tangents to tracks are also extrapolated
to the ECAL from the interaction points between the track and each tracker layer, and clusters can be 
linked to the track as a possible bremsstrahlung photon if the extrapolated tangent
position is within the boundaries of the cluster.
Links between calorimeter clusters are made when the cluster position in the
more granular calorimeter is within the cluster of the less granular calorimeter,
with the link distance again defined as the $\Delta R$ between the positions of the two clusters.
To determine links between charged tracks in the inner tracker and a muon track
in the muon system, a global fit between the two tracks is performed, where the link
is accepted if requirements on the maximum $\chi^2$ of this fit are met. This
$\chi^2$ also determines the distance parameter.

@@

\section{Missing energy}
\label{sec:objects_met}
The \ac{CMS} detector is able to detect most stable and long-lived particles,
however, neutrinos and hypothetical neutral weakly interacting particles
travel straight through the detector without being recorded. These particles
will give rise to an energy imbalance in the transverse plane, and so their
presence can be inferred from missing energy, \MET, in the event.

The \MET~is defined as $-\Sigma \vec{p}_{\text{T}}$, where
the sum runs over all final-state particles and jets in the event. This quantity
can be mismeasured due to detector inefficiencies, calorimeter energy thresholds and
the nonlinearity of the calorimeter
response for hadronic particles.
Therefore, to increase the accuracy of the \MET~measurement the jet energy corrections are propagated as
\begin{equation}\label{eqn:objects_met_corr}
\vec{E}_{\text{T}}^{\text{miss, corr}} = \vec{E}_{\text{T}}^{\text{miss}} - \Sigma_{jets} (\vec{p}_{\text{T,jet}}^{\text{  corr}} - p_{\text{T,jet}}).
\end{equation}

%The magnitude of the ⃗E/T can be underestimated or overestimated for a variety of reasons, including minimum energy thresholds in the calorimeters, pT thresholds and inefficiencies in the tracker, and the nonlinearity of the response of the calorimeter for hadronic particles due to its non-compensating nature. This bias is significantly reduced by correcting the pT of jets to the particle-level pT using jet energy corrections 
The \MET~can also be mismeasured due to pileup interactions, and an improved
measurement of the \MET~at high pileup can be obtained by using the MVA \MET~
algorithm, used for \MET~reconstruction in the analyses presented in chapters \ref{chap:hhh} and 
\ref{chap:mssm}. This algorithm computes a correction to the hadronic
recoil $\vec{u}_{\text{T}}$ reconstructed from \ac{PF} particles
\begin{equation}\label{eqn:objects_met_recoil}
\vec{u}_{\text{T}} = \vec{E}_{\text{T}}^{\text{miss}} - \Sigma \vec{p}_{\text{T}}^{\text{  lep}},
\end{equation}
where $\Sigma \vec{p}_{\text{T}}^{\text{  lep}}$ corresponds to the vectorial sum of the transverse momenta of the
constituents selected as the di-tau candidate.

@@

In the process of calculating the corrections to the hadronic recoil using the MVA \MET~algorithm, an event-by-event
estimator of the likelihood that the \MET~is due to unseen objects rather than induced
by mismeasurement of jet energy is also determined \cite{cms-met-run1}.
%Further corrections improve the performance of the ⃗E/T reconstruction in events with large numbers of pileup interactions. The contribution to the genuine ⃗E/T from such interactions is
%close to zero, as the probability to produce neutrinos is small in inelastic pp scattering (mini- mum bias) interactions. The vectorial ⃗pT sum of charged particles is therefore expected to be well balanced by that of neutral particles. However, the nonlinearity and minimum energy thresholds in the calorimeters cause ⃗E/ T to point on average in the direction of the vectorial ⃗pT sum of neutral particles.

\subsection{Recoil corrections}
\label{sec:objects_met_recoilcorr}
To correct for the mismodelling of \MET~in simulated events, recoil corrections are determined. 
The hadronic recoil $\vec{u}_{\text{T}} = \vec{E}_{\text{T}}^{\text{miss}} - \Sigma \vec{p}_{\text{T}}^{\text{ leptons}/\nu}$ 
is projected onto the axes parallel, $u_{\parallel}$, and perpendicular, $u_{\perp}$, to the \pT~of the boson producing the leptons
and neutrinos. For the analyses
presented in chapters \ref{chap:hhh} and \ref{chap:mssm} it is measured in \Zmm events, where no neutrinos
are present. Distributions of $u_{\parallel}$ and $u_{\perp}$ are fitted both in data
and simulated events, using convolutions of gaussians. Corrections are then applied to the simulation
as
\begin{equation}\label{eqn:met_recoilcorr}
u_{\parallel,\perp}' = <u_{\parallel,\perp}>_{\text{data}} + (u_{\parallel,\perp} - <u_{\parallel,\perp}>_{\text{MC}}) \cdot \frac{\sigma_{\text{Data}}}{\sigma_{\text{MC}}}.
\end{equation}
%Recoil corrections are applied to correct for the mismodelling of $\MET$ in events without genuine $\MET$ \cite{RecoilCorrPresentation}.
%The hadronic recoil is defined as
%$\vec{U} = \vec{E}_{\text{T}}^{mis} - \Sigma \vec{p}_{\text{T},\nu/lep}$. This recoil is projected onto the axes parallel ($U_1$) and
%orthogonal ($U_2$) to the boson $p_{\text{T}}$ and it is measured in $Z\rightarrow\mu\mu$ events, in which the $\nu$ term is 0. Events are selected
%by requiring the HLT\_IsoMu22\_v trigger in data, and opposite--sign muon pairs are selected by requiring two muons with opposite charge, passing
%the medium HIP safe muon ID, the same impact parameter cuts as in the muon selection for the analysis, $I_{rel}^{\mu} < 0.15$. The leading
%muon must have a $p_{\text{T}}$ of at least 23 GeV, with the trailing muon having a $p_{\text{T}}$ of at least 10 GeV. In addition, for data
%events the leading muon must have fired the HLT\_IsoMu22\_v trigger. The requirements on muon $\eta$ are $|\eta_1| < 2.1$ and $|\eta_2|<2.4$.
%At pair level, the two muons must be separated by $\Delta R > 0.5$, and the di-muon mass must be at least 20 GeV. Pile--up reweighting,
%the muon ID, isolation, and trigger scale factors are applied, as are the muon tracking efficiencies. The DY shape reweighting
%is applied to DY MC and top $p_{T}$ reweighting is applied to the $t\bar{t}$ MC.
%The projected hadronic recoil $U$
%is determined for both $Z\rightarrow\mu\mu$ data and MC events. A double gaussian with means symmetrically shifted away from zero is used to fit the $U_2$ component,
%with a triple  gaussians for fitting the $U_1$ component. These fits are performed in bins of $Z p_{\text{T}}$ (0-10, 10-20, 20-30, 30-50, and $ > 50$ GeV), and
%bins of number of jets (0, 1 or at least 2). $Z\rightarrow \mu\mu$ events from around the Z peak are used by requiring $70 <m_{\mu\mu} < 110 $ GeV.
%To apply the corrections, the offset $w = U{1,2} -<U_{1,2}>_{MC} $ and the recoil in MC is corrected as
%$U_{1,2}' = <U_{1,2}>_{data} + w\frac{\sigma_{data}}{\sigma_{MC}}$.

>>>>

For a particle to be identified as an electron it 
must also be reconstructed as an electron by the \ac{PF} algorithm, 
and must in addition pass more advanced identification criteria based on some of the variables used in the
standalone electron reconstruction. This provides separation power from backgrounds
such as photon conversions, jets misidentified as electrons, or electrons from b- and c-quark
decays. Both a cut-based algorithm and an algorithm based on \acp{BDT} are available. %FIXME define BDT
For the selection of electrons in 
the analyses presented in later chapters the \ac{BDT}-based algorithm is used, 
with exceptions for the loose identification criteria required for vetoing electrons. 
The variables used in this \ac{BDT} include:%FIXME full stop usage?!
\begin{itemize}
\setlength{\itemsep}{-0.5\baselineskip}
\item Cluster shape variables, such as $\sigma_{i\eta,i\eta}$, the energy-weighted width of the supercluster in units of $\eta$ crystals (illustrated in figure \ref{fig:ele_id_vars}a). 
\item Track quality variables.
\item Distances in $\eta$ and $\phi$ between the supercluster and the associated track.
\item Energy ratios and energy-momentum ratios in the region of the supercluster, including
$1/E_{\text{SC}} - 1/p_{\Pe}$, where $E_{\text{SC}}$ is the energy in the supercluster and $p_{\Pe}$ the momentum of the electron track (illustrated in figure \ref{fig:ele_id_vars}b).
%\item Cluster shape variables $\sigma_{i\eta,i\eta}$ and $\sigma_{i\phi,i\phi}$, with $i\eta$ and $i\phi$ the integer
%label of the $\eta$ and $\phi$ calorimeter cell. The circularity =  $1 -\frac{E1\times5}{E5\times5}$, with
%$E1\times5$ and $E5\times5$ the energies in a $1\times5$ and a $5\times5$ grid around the super cluster seed,
%respectively. Shape variable R9 = $\frac{E3\times3}{E_{SC}}$, with $E3\times3$ the energy in a $3\times3$ grid
%of cells around the super cluster seed and $E_{SC}$ the raw energy of the super cluster.
%\item The number of valid hits in the track fit, the $\chi^2$ of the track fit and the $\chi^2$ of the GSFTrack fit
%%\item The number of GSFtrack hits, the number of expected missing inner hits and the result of the conversion vertex fit
%\item The distance $\Delta \eta$ and $\Delta \phi$ between the reconstructed super cluster and the associated track at the position of the primary vertex, and the distance in $\eta$ between the super cluster and the track at the calorimeter surface.
%\item H/E, the ratio of the hadronic energy over the electromagnetic energy in the super cluster and E/P, the ratio of the super cluster energy over the momentum of the track associated with the electron
%\item The ratio of the energy of the electron cluster and the momentum of the associated track, evaluated at the electron cluster,
% and $1/E_e - 1/P_e$, with $E_e$ the energy of the electron candidate and $P_e$ its momentum.
\end{itemize}
%Figure \ref{fig:ele_id_vars} shows the distributions of $\sigma_{i\eta,i\eta}$ and $1/E_{sc} - 1/p_e$ 
%for real and misidentified electrons in the full dataset from the 2012 running period of the \ac{LHC}.

\begin{figure}[h!]
\begin{center}
\subfloat[$\sigma_{i\eta,i\eta}$]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/Sigmaietaieta.png}}
\subfloat[$1/E_{\text{SC}} - 1/p_{e}$]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/OneoverEminOneoverp.png}}
\end{center}
\caption[$\sigma_{i\eta,i\eta}$ and $1/E_{\text{SC}}-1/p_{e}$ for real 
and misidentified electrons at $8\,\TeV$, for data and simulation.]{(a) $\sigma_{i\eta,i\eta}$ and (b) $1/E_{\text{SC}} - 1/p_{e}$ for real (black points)  and 
misidentified (yellow triangles) electrons in a dataset corresponding to $19.7\,\invfb$
taken at $\sqrt{s} = 8\,\TeV$, overlaid on the distributions for simulated 
real electrons in purple \cite{cms-elereco-run1}.}
\label{fig:ele_id_vars}
\end{figure}

@@

For the analysis presented in chapter \ref{chap:mssm}, ``medium'' muon requirements were applied \cite{CMS-PAS-HIG-16-037}.
These requirements include:
\begin{itemize}
\setlength{\itemsep}{-0.5\baselineskip}
\item Reconstruction by either the global or tracker muon reconstruction algorithms.
\item Requirements on track quality, and compatibility between the tracker track and the muon system track.
\item Selection on the segment compatibility, a weight between 0 and 1 which is a measure of the compatibility
of a track with the muon track segments in the muon stations it has crossed.
\item Requirements on the maximum kink in the tracker track in any of the layers of the tracker, to suppress in-flight decays.
\end{itemize}
%Apart from having passed either the global or tracker muon reconstruction, the selection
%includes a threshold on the fraction of valid tracker hits, requirements on the
%$\chi^2$/$N_{\text{dof}}$ of the global track fit, on the compatibility of the tracker- and standalone-reconstructed
%position matching, on the kink finder in the inner tracker, and the segment compatibility. 
%The compatibility of the tracker- and standalone-reconstructed position is evaluated
%by extrapolating both the muon track and the tracker track to the same surface and evaluating the $\chi^2$ 
%compatibility there.
%The kink finder determines the $\chi^2$ compatibility between the positions of the outward- and inward interpolated
%tracks in each layer of the inner tracker. The largest $\chi^2$ value found at any of the tracker layers 
%is used as a discriminator. If the $\chi^2$ value is large, this could signal an in--flight decay.
%The segment
%compatibility is a weight between 0 and 1 which is a measure of the compatibility of a track with
%the muon track segments in muon stations it has crossed. Numbers closer to 1 represent
%a greater compatibility of the track with the muon segments, and therefore with the track belonging to a muon.
%MEDIUM REQUIREMENTS
%To pass the identification, global- or tracker muons
%with a large enough fraction of tracker hits must pass \textbf{either} 
%\begin{itemize}
%\setlength{\itemsep}{-\baselineskip}
%\item The muon is reconstructed by the global muon reconstruction algorithm
%\item The $\chi^2$/$N_{\text{dof}}$ of the global track fit, using both the tracker and muon system hits, should be less than 3
%\item The $\chi^2$ compatibility of the tracker-standalone position is smaller than 12
%\item The $\chi^2$ compatibility of the kink finder in the tracker is less than 20
%\item The segment compatibility is $>$ 0.303
%\end{itemize}
%\textit{or}:
%\begin{itemize}
%\setlength{\itemsep}{-\baselineskip}
%\item The segment compatibility is $>$ 0.451
%\end{itemize}

@@

The \ac{PF} algorithm starts from charged particle tracks measured
by the inner tracker, muon tracks measured in the muon system, and 
energy deposits in the calorimeters. These energy deposits are combined
using a clustering algorithm, so that stable neutral particles can be identified and
separated from charged hadrons, and in addition electrons and all bremsstrahlung photons
can be reconstructed. Clustering is performed separately in the \ac{ECAL} barrel,
\ac{ECAL} endcaps, first and second preshower layers, \ac{HCAL} barrel and \ac{HCAL} endcaps, with no 
clustering employed in the \ac{HF}.
%And to aid energy measurement of charged hadrons for which
%tracks were low quality, or high pT
The clustering algorithm used for \ac{PF} starts from cluster seeds,
calorimeter cells with local energy maxima. Topological clusters are built by 
merging neighbouring cells into the cluster, provided that the cells
being merged in contain a certain minimum energy.
The threshold is $800\,\MeV$ in the \ac{HCAL} and two standard deviations above the
expected noise level in the \ac{ECAL}, meaning $80\,\MeV$ in the barrel and up 
to $300\,\MeV$ in the endcaps. Cell energies can be shared between multiple
\ac{PF} clusters, depending on the distance between a cell and the centre of the cluster.

Any given particle will usually give rise to multiple \ac{PF}
elements in the different subdetectors. To provide full reconstruction
of each particle, and avoid double counting, the next step in the
\ac{PF} algorithm is to link the different elements. This is
achieved by defining a distance parameter between any two \ac{PF} elements
in the event, which quantifies the link quality. Directly and indirectly
linked elements are considered as input blocks to the reconstruction and
identification algorithm. Links between charged tracks and calorimeter
clusters are established by extrapolating the track from its last measured
tracker hit to the preshower layers, the \ac{ECAL} and the \ac{HCAL}. %in ECAL to expected maximum of a 
%typical longitudinal electron shower profile and in the HCAL at a depth correspnding to one interaction
%length.
If the extrapolated track position is within the boundaries of the cluster, plus the size
of one cell in each direction to account for gaps between cells and multiple scattering, the
track is said to be linked to the calorimeter cluster. The link distance parameter 
is taken as the distance $\Delta R$ 
between the position of the cluster and the position of the track. Tangents to tracks are also extrapolated
to the ECAL from the interaction points between the track and each tracker layer, and clusters can be 
linked to the track as a possible bremsstrahlung photon if the extrapolated tangent
position is within the boundaries of the cluster.
Links between calorimeter clusters are made when the cluster position in the
more granular calorimeter is within the cluster of the less granular calorimeter,
with the link distance again defined as the $\Delta R$ between the positions of the two clusters.
To determine links between charged tracks in the inner tracker and a muon track
in the muon system, a global fit between the two tracks is performed, where the link
is accepted if requirements on the maximum $\chi^2$ of this fit are met. This
$\chi^2$ also determines the distance parameter.

@@

\section{Missing energy}
\label{sec:objects_met}
The \ac{CMS} detector is able to detect most stable and long-lived particles,
however, neutrinos and hypothetical neutral weakly interacting particles
travel straight through the detector without being recorded. These particles
will give rise to an energy imbalance in the transverse plane, and so their
presence can be inferred from missing transverse energy, \MET, in the event.

The \MET~is defined as $-\Sigma \vec{p}_{\text{T}}$, where
the sum runs over all final-state particles and jets in the event. This quantity
can be mismeasured due to detector inefficiencies, calorimeter energy thresholds and
the nonlinearity of the calorimeter
response for hadronic particles.
Therefore, to increase the accuracy of the \MET~measurement the jet energy corrections are propagated as
\begin{equation}\label{eqn:objects_met_corr}
\vec{E}_{\text{T}}^{\text{miss, corr}} = \vec{E}_{\text{T}}^{\text{miss}} - \Sigma_{jets} (\vec{p}_{\text{T,jet}}^{\text{  corr}} - \vec{p}_{\text{T,jet}}),
\end{equation}
where `corr' refers to the corrected values.
%The magnitude of the ⃗E/T can be underestimated or overestimated for a variety of reasons, including minimum energy thresholds in the calorimeters, pT thresholds and inefficiencies in the tracker, and the nonlinearity of the response of the calorimeter for hadronic particles due to its non-compensating nature. This bias is significantly reduced by correcting the pT of jets to the particle-level pT using jet energy corrections 
The \MET~can also be mismeasured due to pileup interactions, and an improved
measurement of the \MET~at high pileup can be obtained by using the MVA \MET~
algorithm, used for \MET~reconstruction in the analyses presented in chapters \ref{chap:hhh} and 
\ref{chap:mssm}. This algorithm computes a correction to the hadronic
recoil $\vec{u}_{\text{T}}$ reconstructed from \ac{PF} particles
\begin{equation}\label{eqn:objects_met_recoil}
\vec{u}_{\text{T}} = \vec{E}_{\text{T}}^{\text{miss}} - \Sigma \vec{p}_{\text{T}}^{\text{  lep}},
\end{equation}
where $\Sigma \vec{p}_{\text{T}}^{\text{  lep}}$ corresponds to the vectorial sum of the transverse momenta of the
constituents selected as the di-tau candidate.

In the process of calculating the corrections to the hadronic recoil using the MVA \MET~algorithm, an event-by-event
estimator of the likelihood that the \MET~is due to unseen objects rather than induced
by mismeasurement of jet energy is also determined~\cite{cms-met-run1}.

@@

%Further corrections improve the performance of the ⃗E/T reconstruction in events with large numbers of pileup interactions. The contribution to the genuine ⃗E/T from such interactions is
%close to zero, as the probability to produce neutrinos is small in inelastic pp scattering (mini- mum bias) interactions. The vectorial ⃗pT sum of charged particles is therefore expected to be well balanced by that of neutral particles. However, the nonlinearity and minimum energy thresholds in the calorimeters cause ⃗E/ T to point on average in the direction of the vectorial ⃗pT sum of neutral particles.

\subsection{Recoil corrections}
\label{sec:objects_met_recoilcorr}
To correct for the mis-modelling of \MET~in simulated events, recoil corrections are determined. 
The hadronic recoil $\vec{u}_{\text{T}} = \vec{E}_{\text{T}}^{\text{miss}} - \Sigma \vec{p}_{\text{T}}^{\text{ leptons}/\nu}$ 
is projected onto the axes parallel, $u_{\parallel}$, and perpendicular, $u_{\perp}$, to the \pT~of the boson producing the leptons
and neutrinos. For the analyses
presented in chapters \ref{chap:hhh} and \ref{chap:mssm} it is measured in \Zmm events, where no neutrinos
are present. Distributions of $u_{\parallel}$ and $u_{\perp}$ are fitted both in data
and simulated events, using convolutions of gaussians. Corrections are then applied to the simulation
as
\begin{equation}\label{eqn:met_recoilcorr}
u_{\parallel,\perp}' = <u_{\parallel,\perp}>_{\text{data}} + (u_{\parallel,\perp} - <u_{\parallel,\perp}>_{\text{MC}}) \cdot \frac{\sigma_{\text{Data}}}{\sigma_{\text{MC}}}.
\end{equation}
%Recoil corrections are applied to correct for the mismodelling of $\MET$ in events without genuine $\MET$ \cite{RecoilCorrPresentation}.
%The hadronic recoil is defined as
%$\vec{U} = \vec{E}_{\text{T}}^{mis} - \Sigma \vec{p}_{\text{T},\nu/lep}$. This recoil is projected onto the axes parallel ($U_1$) and
%orthogonal ($U_2$) to the boson $p_{\text{T}}$ and it is measured in $Z\rightarrow\mu\mu$ events, in which the $\nu$ term is 0. Events are selected
%by requiring the HLT\_IsoMu22\_v trigger in data, and opposite--sign muon pairs are selected by requiring two muons with opposite charge, passing
%the medium HIP safe muon ID, the same impact parameter cuts as in the muon selection for the analysis, $I_{rel}^{\mu} < 0.15$. The leading
%muon must have a $p_{\text{T}}$ of at least 23 GeV, with the trailing muon having a $p_{\text{T}}$ of at least 10 GeV. In addition, for data
%events the leading muon must have fired the HLT\_IsoMu22\_v trigger. The requirements on muon $\eta$ are $|\eta_1| < 2.1$ and $|\eta_2|<2.4$.
%At pair level, the two muons must be separated by $\Delta R > 0.5$, and the di-muon mass must be at least 20 GeV. Pile--up reweighting,
%the muon ID, isolation, and trigger scale factors are applied, as are the muon tracking efficiencies. The DY shape reweighting
%is applied to DY MC and top $p_{T}$ reweighting is applied to the $t\bar{t}$ MC.
%The projected hadronic recoil $U$
%is determined for both $Z\rightarrow\mu\mu$ data and MC events. A double gaussian with means symmetrically shifted away from zero is used to fit the $U_2$ component,
%with a triple  gaussians for fitting the $U_1$ component. These fits are performed in bins of $Z p_{\text{T}}$ (0-10, 10-20, 20-30, 30-50, and $ > 50$ GeV), and
%bins of number of jets (0, 1 or at least 2). $Z\rightarrow \mu\mu$ events from around the Z peak are used by requiring $70 <m_{\mu\mu} < 110 $ GeV.
%To apply the corrections, the offset $w = U{1,2} -<U_{1,2}>_{MC} $ and the recoil in MC is corrected as
%$U_{1,2}' = <U_{1,2}>_{data} + w\frac{\sigma_{data}}{\sigma_{MC}}$.
